---
title: "NHANES EDA"
author: "Kevin S.W. --- UNI: ksw2137"
date: "`r format(Sys.time(), '%x')`"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# global default settings for chunks
knitr::opts_chunk$set(echo = TRUE, #eval = FALSE,
                      fig.dim = c(10, 4), 
                      fig.align = "center",
                      results = "asis"
                      )

# loaded packages; placed here to be able to load global settings
Packages <- c("tidyverse", "dplyr")
invisible(lapply(Packages, library, character.only = TRUE))

# global settings for color palettes
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

# theme global setting for ggplot
theme_set(theme_minimal() + 
            theme(legend.position = "bottom") +
            theme(plot.title = element_text(hjust = 0.5, size = 12),
                  plot.subtitle = element_text(hjust = 0.5, size = 8))
          )

```

# NHANES Dataset EDA

Purpose of this project is to explore what the dataset contains and if it is workable. Further exploration will be decided based on these possibilities. 

## Loading Dataset

```{r dataload}

# devtools::install_github("andrew-leroux/rnhanesdata")
library(rnhanesdata)

```

Based on the vignette? provided by the author, it seems that there are 2 main "dataset-packs" contained in the package categorized below. Note that all of these datasets are separated by each "waves" where `_C` indicates wave 3 (2003-2004) while `_D` indicates wave 4 (2005-2006).

* Processed:
  * [`PAXINTEN_C` & `PAXINTEN_D`](#accelerometer-data): accelerometry data for 2003-2004 and 2005-2006 respectively. 
  * [`Flags_C` & `Flags_D`](#flags-data): Wear/non-wear flags for 2003-2004 and 2005-2006 respectively. 
  * [`Covariate_C` & `Covariate_D`](#covariate-data): Additional NHANES dataset containing other covariates recorded in the raw data for 2003-2004 and 2005-2006 respectively. 
  * `Mortality_2011_C` & `Mortality_2011_D`: mortality info for 2003-2004 and 2005-2006 respectively from NHANES database that were processed; released in 2011. 
* Raw:
  * `ALQ_C` & `ALQ_D`: alcohol consumption dataset from 2 "waves" of datasets (exists in Covar)
  * `BMX_C` & `BMX_D`: body measurement datasets from 2 waves. 
  * `BPX_C` & `BPX_D`: blood pressure data from the 2 waves.
  * `DEMO_C` & `DEMO_D`: demographic data
  * `DIQ_C` & `DIQ_D`: diabetes questionnaire data
  * `MCQ_C` & `MCQ_D`: medical conditions questionnaire
  * `PFQ_C` & `PFQ_D`: physical function questionnaire data
  * `SMQ_C` & `SMQ_D`: smoking status questionnaire
  * `NHANES_2003-2004_MORT_2011_PUBLIC`
  * `NHANES_2005-2006_MORT_2011_PUBLIC`

 We are going to explore these processed dataset and see what can be done with it. Unfortunately, the raw data were inaccessible without using the package's functions and I wasn't too familiar yet with this. Although it seems that data 

# Processed Data Exploration

## [Accelerometer Data](#loading-dataset)

```{r accel_data}

# Data import for accelerometry data from wave C (2003-2004)
nested_accel1 <- PAXINTEN_C %>% 
  janitor::clean_names() %>% 
#  pivot_longer(cols = starts_with("MIN"), 
#               names_to = "min",
#               names_prefix = "min",
#               values_to = "activ_count") %>% 
#  mutate(
#    min = as.numeric(min)
#  ) %>% 
  mutate_at(
    .vars = vars("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"),
    .funs = funs(factor)
  ) %>% 
  group_by(seqn) %>% 
  nest(accel_mins = min1:min1440) %>% 
  nest(wave_C = paxcal:accel_mins)


# Data import for accelerometry data from wave D (2005-2006)
accel2 <- PAXINTEN_D %>% 
  janitor::clean_names() %>% 
#  pivot_longer(cols = starts_with("MIN"), 
#               names_to = "min",
#               names_prefix = "min",
#               values_to = "activ_count") %>% 
#  mutate(
#    min = as.numeric(min)
#  ) %>% 
  mutate_at(
    .vars = vars("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"),
    .funs = funs(factor)
  ) %>% 
  group_by(seqn) %>% 
  nest(accel_mins = min1:min1440) %>% 
  nest(wave_D = paxcal:accel_mins)

```
  
Both of these datasets contain similar variables. Of primary focus:

* `SEQN`: Unique ID
* `PAXCAL`: Device calibration with 1 = yes, 2 = no, 9 = unknown
* `PAXSTAT`: Data reliability status with 1 = reliable, 2 = questionable
* `SDDSRVYR`: Indicates which "wave" the data comes from. 3 means from 2003-2004, 4 = 2005-2006
* `WEEKDAY`: Day of the week with 1 as Sunday, 7 as Saturday.
* `MIN`: Activity count at each minute of the day.  

Taking wave C's data and checking each variable using skimr reveals that paxcal has 3 unique values and paxstat has 2 values which suggests that some of these values are either "uncalibrated", "questionable", or "unknown". This might require further filtering.

```{r skimr_accel, eval = FALSE}

accel1 %>% 
  select(-min) %>% 
  skimr::skim_without_charts()

```

We also merged wave C and D to see if all these data are continuously recorded for the same people. Will utilize nesting as well to minimize load on PC.  

```{r joined_accel_data}

# combining 2 datasets based on seqn, the unique ID
joined_accel <- full_join(nested_accel1, nested_accel2, by = "seqn")

# counts distinct seqn's based on the unique ID
joined_accel %>% 
  ungroup() %>% 
  distinct(seqn) %>% 
  count()

```

Per our "nested" findings, it was surprising to see that the `seqn` are all unique from wave C to D. In other words, we have a total of `nrow(joined_accel)` unique observations, which are all from different people. If we were to just aggregate these, we could likely ignore the wave ID if time were not considered. 

**NOTE: Working with a single wave dataset may take up to 5GB of RAM**

The function `process_accel` seems to be able to interact with CDC's data directly and therefore capable of obtaining more recent data if needed. 

## [Flags Data](#loading-dataset)

```{r flags_data}

flag1 <- Flags_C %>% 
  janitor::clean_names() %>% 
#  pivot_longer(cols = starts_with("MIN"), 
#               names_to = "min",
#               names_prefix = "min",
#               values_to = "flag_indicator") %>% 
#  mutate(
#    min = as.numeric(min)
#  ) %>% 
  mutate_at(
    .vars = vars("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"),
    .funs = funs(factor)
  ) %>% 
  group_by(seqn) %>% 
  nest(flag_mins = min1:min1440) %>% 
  nest(wave_C = paxcal:flag_mins)


flag2 <- Flags_D %>% 
  janitor::clean_names() %>% 
#  pivot_longer(cols = starts_with("MIN"), 
#               names_to = "min",
#               names_prefix = "min",
#               values_to = "flag_indicator") %>% 
#  mutate(
#    min = as.numeric(min)
#  ) %>% 
  mutate_at(
    .vars = vars("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"),
    .funs = funs(factor)
  ) %>% 
  group_by(seqn) %>% 
  nest(flag_mins = min1:min1440) %>% 
  nest(wave_D = paxcal:flag_mins)

```

The flags data appear to be a very detailed, minute-by-minute indicator of whether or not the device was worn by that particular person as identified by their `seqn`. These numbers are equivalent to the number of data points observed in accelerometer. **Besides the minute tracking of wear flags, other variables are the same as those found in accelerometer data.** 

We can also nest these data since "flag_dataset" is capable of being its own dataset. Since flag and accelerometer data are related, we could probably join these datasets based on the unique `seqn` identifier and have everything in 1 "table"

**NOTE: working with accelerometer AND flag data consumes a large amount of RAM (~10 GB)**

The function `process_flags` from the package allows the "raw" data obtained from `process_accel` and isolate just the wear variables. 

## [Covariate Data](#loading-dataset)

Based on the vignette? it appears that the raw NHANES data beyond accelerometry are collated within the "covariates data". This will be explored further below.

```{r covar_data}

covar1 <- Covariate_C %>% 
  janitor::clean_names()
  

covar2 <- Covariate_D %>% 
  janitor::clean_names()

```

Unlike flag and accelerometer data, these covar data are not structured similarly to the other two and therefore might benefit from being a separate dataset. Unique identifier still exist and thus can be joined if necessary. This will be easily possible if we can maintain nested dataset of both flag and accelerometer. 

Additionally, the amount of `seqn` observations in the covariates are more than `seqn` within flag and accelerometer. We should left join this if we plan to merge the datasets. 

Furthermore, the covariates inside were not the complete covariates from the NHANES raw data. In these "cleaned" dataset, covariates are:

* `SDDSRVYR`: Wave indicator as in other datasets
* `SDMVPSU`: Masked variance pseudo probability sampling units. Used for variance estimation??
* `SDMVSTRA`: Masked variance pseudo stratum. Used for variance estimation??
* `WTINT2YR`: Full sample interviewed weight (likely reported weight)
* `WTMEC2YR`: Full sample examination weight (likely observed weight)
* `RIDAGEMN`: Age in months at screening date for those < 85 years. >= 85 is coded as NA
* `RIDAGEEX`: Age in months at examination date for those < 85 years. >= 85 is coded as NA
* `RIDAGEYR`: Age in years at date of screening
* `BMI`: BMI in kg/m^2. A copy of BMXBMI variable.
* `BMI_cat`: Category for the BMI values. underweight (<= 18.5), normal (18.5 < x <= 25), overweight (25 < x <= 30), obese (> 30)
* `Race`: Self-reported ethnicity
* `Gender`: Self-reported gender for M/F
* `Diabetes`: Self-reported diagnosed diabetes, categorized to Yes, No, Borderline, Refused, Don't know. 
* CHF
* CHD
* Cancer
* Stroke
* MobilityProblem
* DrinkStatus
* DrinksPerWeek
* SmokeCigs

# Raw Data Exploration

Based on the package, it appears that the raw NHANES data primarily contributes to the covariate data. Using a function from within the `rnhanesdata` package, `process_covar()`, we're able to interact with the raw NHANES data within the package and obtain all available covariates. 

```{r covar_raw_data}

# extract raw NHANES data and convert to tibble
covar_data_C <- as_tibble(
  process_covar(
    waves = "C", extractAll = TRUE
    )[[1]] # process_covar outputs a list of 1 containing the tibble, this extracts the "content" and 
  )        # turn it into tibble

```

Playing around with the function from the package unfortunately only reveals that the dataset included only ranges from wave C (2003-2004) & D (2005-2006). However, it appears that if we could obtain .XPT files from more recent datasets, we could process it similarly. 

*Self-question: Why does, given a list of tibble, using tibble vs data.frame differs in the results? The covar_data_C is a list structure where it it spits out a list of 1 that contains a list of 383 variables that each contains a "list" of the observations*
