---
title: "Cleaned Dataset Exploration"
author: "Kevin S.W. --- UNI: ksw2137"
date: "`r format(Sys.time(), '%x')`"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# global default settings for chunks
knitr::opts_chunk$set(echo = TRUE, 
                      fig.dim = c(10, 4), 
                      fig.align = "center",
                      results = "asis"
                      )

# loaded packages; placed here to be able to load global settings
Packages <- c("tidyverse", "dplyr")
invisible(lapply(Packages, library, character.only = TRUE))



# global settings for color palettes
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

# theme global setting for ggplot
theme_set(theme_minimal() + 
            theme(legend.position = "bottom") +
            theme(plot.title = element_text(hjust = 0.5, size = 12),
                  plot.subtitle = element_text(hjust = 0.5, size = 8))
          )

```


# Exploration of Data Distribution by Outcome Variable

```{r}

nhanes_df <- read_csv("./Datasets/cleaned_dataset.csv") %>% 
  mutate(across(where(is.character), factor))

```

## Continuous Variables

## Categorical Variables

### Gender

This variable is to identify the gender. Coded as `1=male` and `2=female` but we recoded this for easier interpretation. We then observe the difference of diabetes prevalence between the two groups

```{r}

nhanes_df %>% 
  group_by(gender) %>% 
  count(diabetes) %>% 
  ggplot(aes(x = diabetes, y = n, color = gender, fill = gender)) + 
  geom_bar(stat = "identity", alpha = 0.5, position = "dodge")

```


### `ridreth1`: Ethnicity/race.  

This is the variable to describe race. The categories are:
  
1. Mexican American  
2. Other Hispanic  
3. Non-Hispanic White  
4. Non-Hispanic Black  
5. Other (incl. multi-racial)  

```{r}

nhanes_df %>% count(race_eth)

```

As seen above, it seems that we have a "complete" data for this variable.

```{r}

nhanes_df %>% 
  group_by(race_eth) %>% 
  count(diabetes) %>% 
  ggplot(aes(x = diabetes, y = n, color = race_eth, fill = race_eth)) + 
  geom_bar(stat = "identity", alpha = 0.5, position = "dodge") +
  facet_wrap(~ race_eth)

```

### `bpxpuls`: quality of pulse  

```{r}

nhanes_df %>% count(pulse)

nhanes_df %>% 
  group_by(pulse) %>% 
  count(diabetes) %>% 
  ggplot(aes(x = diabetes, y = n, color = pulse, fill = pulse)) + 
  geom_bar(stat = "identity", alpha = 0.5, position = "dodge")

```

Exploring our dataset, we notice that there are some `NA` values contained in this variable. These likely correspond to participants that did not have their vitals measured. These will likely be removed. 

# `diq050`: Is subject taking insulin currently
