---
title: "`rnhanesdata` Exploration"
output: 
  html_document:
    theme: flatly
    highlight: pygments
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# global default settings for chunks
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
                      fig.dim = c(10, 4), 
                      fig.align = "center"
                      )

# loaded packages; placed here to be able to load global settings
Packages <- c("tidyverse", "dplyr")
invisible(lapply(Packages, library, character.only = TRUE))



# global settings for color palettes
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

# theme global setting for ggplot
theme_set(theme_minimal() + 
            theme(legend.position = "bottom") +
            theme(plot.title = element_text(hjust = 0.5, size = 12),
                  plot.subtitle = element_text(hjust = 0.5, size = 8))
          )

```

This section details my exploration of the `rnhanesdata` package that was the initial objective of my project (which evolved into something else eventually). This was the earliest attempt to explore what the dataset contains and whether or not I could develop something out of the provided dataset. 

# Loading Dataset

We first install/load the `rnhanesdata` package.

```{r package load}
# devtools::install_github("andrew-leroux/rnhanesdata")
library(rnhanesdata)
```

## Datasets

The package contains 2 waves of NHANES dataset; 2003-2004 and 2005-2006 (labeled wave C and D, respectively). There are two main categories, "processed" and "raw" datasets. Details below:

* Processed:
  * `PAXINTEN_C` & `PAXINTEN_D`: Accelerometry data
  * `Flags_C` & `Flags_D`: Wear/non-wear flags
  * `Covariate_C` & `Covariate_D`: Additional NHANES dataset containing select, processed covariates. 
  * `Mortality_2011_C` & `Mortality_2011_D`: Processed mortality data.
* Raw:
  * `ALQ_C` & `ALQ_D`: Alcohol consumption dataset
  * `BMX_C` & `BMX_D`: Body measurement datasets
  * `BPX_C` & `BPX_D`: Blood pressure data
  * `DEMO_C` & `DEMO_D`: Demographic data
  * `DIQ_C` & `DIQ_D`: Diabetes questionnaire data
  * `MCQ_C` & `MCQ_D`: Medical conditions questionnaire
  * `PFQ_C` & `PFQ_D`: Physical function questionnaire data
  * `SMQ_C` & `SMQ_D`: Smoking status questionnaire
  * `NHANES_2003-2004_MORT_2011_PUBLIC`: Raw mortality data 2003-2004
  * `NHANES_2005-2006_MORT_2011_PUBLIC`: Raw mortality data 2005-2006

## Functions

In addition to these datasets, the package also contains several functions that are useful to further clean the dataset, re-calculate survey weights, etc. Firstly, the function `process_covar()` allows us to obtain raw data on chosen variables or, if we apply the option `extractAll = TRUE`, to obtain raw data from all possible variables in NHANES waves C & D. 

The function `reweight_accel()` re-calculates 2-year and 4-year survey weights for a dataset after processing/cleaning has been done. 

The function `exclude_accel()` takes in the activity and flag datasets to return indices of days which were considered "good datapoints" from a combination of wear/non-wear flag and NHANES's criteria for data quality.

They also had other functions, `process_accel()` and `process_flags()` with the purpose of downloading accelerometry and flag data from NHANES and formatting the data into a 1440+ format (minute-by-minute).

# Processed Data Exploration

Having seen the contents and functions of `rnhanesdata` package, we will explore the processed data further. Note that we won't explore the raw data. 

## Accelerometer Data

```{r accel data load}
data("PAXINTEN_C")
data("PAXINTEN_D")

# Wave C data clean to remove the min-variables
accelC_id <- PAXINTEN_C %>% 
  janitor::clean_names() %>% 
  mutate(across(c("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"), factor)) %>% 
  select(-starts_with("min"))

# Wave D data clean to remove the min-variables
accelD_id <- PAXINTEN_D %>% 
  janitor::clean_names() %>% 
  mutate(across(c("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"), factor)) %>% 
  select(-starts_with("min"))
```
  
Both of these datasets contain similar variables:

* `SEQN`: Unique subject ID
* `PAXCAL`: Device calibration with 1 = yes, 2 = no, 9 = unknown
* `PAXSTAT`: Data reliability status with 1 = reliable, 2 = questionable
* `SDDSRVYR`: Indicates which wave the data comes from. 3 = 2003-2004, 4 = 2005-2006
* `WEEKDAY`: Day of the week with 1 as Sunday, 7 as Saturday
* `MIN1`- `MIN1440`: Activity count at each minute of the day (1440+ format)

There are `r accelC_id %>% distinct(seqn) %>% count()` unique subjects with the ID ranging between `r min(PAXINTEN_C$SEQN)` - `r max(PAXINTEN_C$SEQN)` for wave C. 

Wave D has `r accelD_id %>% distinct(seqn) %>% count()` unique subjects with the ID ranging between `r min(PAXINTEN_D$SEQN)` - `r max(PAXINTEN_D$SEQN)`. 

As noted from the range between these two waves, it appears that NHANES assumes none of the individuals are repeat-measures i.e. they're all assumed different individuals. A quick summary below using the `skimr::skim_without_charts()` function for wave C

```{r skim accel}
accelC_id %>% skimr::skim_without_charts()
```

```{r remove accel data, include = FALSE}
rm(list=c("PAXINTEN_C", "PAXINTEN_D"))
```

## Flags Data

```{r flags_data}
# load flag data
data("Flags_C")
data("Flags_D")

# Wave C data clean to remove the min-variables
flagC_id <- Flags_C %>% 
  janitor::clean_names() %>% 
  mutate(across(c("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"), factor)) %>% 
  select(-starts_with("min"))

# Wave D data clean to remove the min-variables
flagD_id <- Flags_D %>% 
  janitor::clean_names() %>% 
  mutate(across(c("seqn", "paxcal", "paxstat", "weekday", "sddsrvyr"), factor)) %>% 
  select(-starts_with("min"))
```

The flags data appear to contain similar primary variables as in `PAXINTEN_C` & `PAXINTEN_D`. Slightly different to the activity dataset however, is the measures within the 1440+ format. While the activity dataset has numeric variables, the flags are binary with only `0` (non-wear) or `1` (wear), though there are some `NA` values. 

```{r remove flag data, include = FALSE}
rm(list=c("flagC_id", "flagD_id", "Flags_C", "Flags_D"))
```

## Covariate Data

These covariate datasets appear to only contain a very small portion of all available NHANES data that were selected by the package creator. Nevertheless, it has functions to obtain all possible covariates from wave C & D. 

```{r covar data}
covarC <- Covariate_C %>% 
  janitor::clean_names()
  
covarD <- Covariate_D %>% 
  janitor::clean_names()
```

Interestingly, the covariate datasets have more unique subjects than the accelerometry datasets. Wave C has `r covarC %>% distinct(seqn) %>% count()` unique subjects as opposed to `r accelC_id %>% distinct(seqn) %>% count()` while wave D has `r covarD %>% distinct(seqn) %>% count()` unique subjects as opposed to `r accelD_id %>% distinct(seqn) %>% count()`.

Covariates included in these datasets are: 

* `SDDSRVYR`: Wave indicator as in other datasets
* `SDMVPSU`: Masked variance pseudo probability sampling units used for variance estimation
* `SDMVSTRA`: Masked variance pseudo stratum used for variance estimation
* `WTINT2YR`: Full sample interviewed weight
* `WTMEC2YR`: Full sample examination weight
* `RIDAGEMN`: Age in months at screening date for those < 85 years. >= 85 is coded as NA
* `RIDAGEEX`: Age in months at examination date for those < 85 years. >= 85 is coded as NA
* `RIDAGEYR`: Age in years at date of screening
* `BMI`: BMI in $kg/m^2$
* `BMI_cat`: Category for the BMI values
  * Underweight (<= 18.5)
  * Normal (18.5 < x <= 25)
  * Overweight (25 < x <= 30)
  * Obese (> 30)
* `Race`: Ethnicity; White, Mexican American, Other Hispanic, Black, Other
* `Gender`: Male/female
* `Diabetes`: Diagnosis of diabetes; yes, No, Borderline, Refused, or Don't know
* `CHF`: Diagnosis of CHF; Yes, No, Refused, or Don't know
* `CHD`: Diagnosis of CHD; Yes, No, Refused, or Don't know
* `Cancer`: Diagnosis of any cancer; Yes, No, Refused, or Don't know
* `Stroke`: Diagnosis of stroke; Yes, No, Refused, or Don't know
* `Education_adult`: Education level of adults
  * Less than 9th grade
  * 9th-11th grade
  * High school grad/GED or equivalent
  * Some College or AA degree
  * College graduate or above
  * Refused
  * Don't know
* `Mobility_Problem`: Mobility issues; Any or No difficulty
* `Drink_Status`: Current alcohol consumption; non-, moderate-, or heavy-drinker
* `Drinks_Per_Week`: Number of drinks per week (0 for non-drinker in `Drink_Status`)
* `Smoke_Cigs`: Cigarette smoking status; Never, Former, Current

```{r remove covars, include = FALSE}
rm(list=c("accelC_id", "accelD_id", "covarC", "covarD"))
```

## Mortality Data

Processed mortality data for NHANES, released in 2011 for waves C and D. They have mortality data from 2011 and 2015. We will explore the more recent 2015 data for now. 

```{r mortality data}
mort_2015_c <- Mortality_2015_C %>% 
  janitor::clean_names()

mort_2015_d <- Mortality_2015_D %>% 
  janitor::clean_names()
```

Obtaining the processed mortality table shows a number of unique subjects of `r mort_2015_c %>% distinct(seqn) %>% count()` for wave C and `r mort_2015_d %>% distinct(seqn) %>% count()` for wave D--similar to the number found in covariates data. We also note several new variables besides `SEQN`:

* `eligstat`: eligibility for mortality follow-up. 1 = eligible, 2 = <18 yrs (not available for public), 3 = ineligible
* `MORTSTAT`: indicator for mortality status at f/u time from permth_exm and permth_int. 0 = assumed alive, 1 = assumed deceased, NA = <18 yrs (not available)
* `permth_exm`: time in months when mortality assessment was done (date of mortality assessment)
* `permth_int`: time in months from interview to mortality assessment
* `ucod_leading`: underlying cause of death
* `diabetes_mcod`: diabetes flag from multiple cause of death
* `hyperten_mcod`: hypertension flag from multiple cause of death

```{r remove mortality data, include = FALSE}
rm(list=c("mort_2015_c", "mort_2015_d"))
```

# Obtaining All Covariates

Now that we've assessed the processed datasets, we will evaluate the capability of the functions in obtaining all the covariates. 

```{r get all covariates, results = 'hide'}
covar_data <- process_covar(extractAll = TRUE)

all_covar_c <- covar_data$Covariate_C
all_covar_d <- covar_data$Covariate_D

rm(list=c("covar_data"))
```

Obtaining all covariates reveal that we have `r length(names(all_covar_c))` and `r length(names(all_covar_d))` variables for wave C and D, respectively. This is a huge amount of variables and we won't be able to filter this efficiently if we evaluate them directly. As such, we will likely build a scraping function to obtain names and descriptions for these variables to make evaluation easier. 

To check out how I built the scraping function and what I did with it, go [here]()

```{r remove all covar df, include = FALSE}
rm(list=c("all_covar_c", "all_covar_d"))
```


<br></br>

<div style="text-align: right">[Return to Homepage](../index.html)</div>